### 2020-01-20 ms/ms.tex
Update map R code and minor ms edits

\noindent\small{\textsuperscript{1} Department of Biology, Dalhousie University, Halifax, NS, B3H 4R2, Canada\\}
\small{\textsuperscript{2} Norwegian Institute for Nature Research (NINA), Trondheim, Norway\\}
\small{\textsuperscript{3} Fisheries and Oceans Canada, St. John's, NL, Canada\\}
\small{\textsuperscript{4} Minist\`{e}re des For\^{e}ts, de la Faune et des Parcs, Qu\'{e}bec, QC, Canada\\}
\small{\textsuperscript{5} Fisheries and Oceans Canada, Moncton, NB, Canada\\}
\small{\textsuperscript{6} Fisheries and Oceans Canada, Dartmouth, NS, Canada\\}
\small{\textsuperscript{*} Corresponding author: spardo@dal.ca}

@@

Smolt and adult return abundance estimates originate from a variety of sources.
Estimates from the XXXX populations were obtained using a capture-mark-recapture approach, while
Estimates from the XXXX populations were obtained by direct counts using a XXXX.
... for more details on the . 
For data collection details refer to 
\citet{Venoitt2018} for NL populations, 
\citet{April2018}  for QC populations,
\citet{Jones2014} for NB populations,
and \textbf{REF} for NS populations.

@@

% 1. Main findings
Our findings challenge the narrative that marine survival, specifically survival in the first year at sea, is declining
uniformly throughout the range of Atlantic salmon in the northwest Atlantic.
Temporal trends are not consistent among populations 
. Over the time periods for which data were available, some rivers show positive trends in survival in the
first winter at sea (\So) while other show highly variable yet stable trends, and some even show
declines. We could not assess trends in the second winter at sea (\So) or
proportion returning as grilse (\Pg), as these parameter estimates were highly
uncertain and were strongly influenced by the priors used.
Perhaps there is a need to rethink our understanding of Atlantic salmon
population dynamics in light of the possibility that any real and persistent decline in marine survival was
experienced by some but not all populations, that reductions in survival might
have occurred over a relatively brief period of time and may not longer be ongoing, and that since that
reduction occurred (for a subset of populations) marine survival has
been stable, or even increasing.

>>>>

\noindent\small{\textsuperscript{1} Department of Biology, Dalhousie University, Halifax, NS, Canada\\}
\small{\textsuperscript{2} Norwegian Institute for Nature Research (NINA), Trondheim, Norway\\}
\small{\textsuperscript{3} Fisheries and Oceans Canada, St. John's, NL, Canada\\}
\small{\textsuperscript{4} Minist\`{e}re des For\^{e}ts, de la Faune et des Parcs, Qu\'{e}bec, QC, Canada\\}
\small{\textsuperscript{5} Fisheries and Oceans Canada, Moncton, NB, Canada\\}
\small{\textsuperscript{6} Fisheries and Oceans Canada, Dartmouth, NS, Canada\\}
\small{\textsuperscript{*} Corresponding author: spardo@dal.ca}

@@

Smolt and adult return abundance estimates originate from a variety of sources.
Estimates from the XXXX populations were obtained using a capture-mark-recapture approach, while
Estimates from the XXXX populations were obtained by direct counts using a XXXX.
... for more details on the . 
For data collection details refer to 
\citet{Venoitt2018} for NL populations, 
\citet{April2018}  for QC populations,
\citet{Jones2014} for NB populations,
and \citet{Gibson2009} for NS populations.

@@

% 1. Main findings
Our findings challenge the narrative that marine survival, specifically survival in the first year at sea, is declining
uniformly throughout the range of Atlantic salmon in the northwest Atlantic.
Temporal trends are not consistent among populations. 
Over the time periods for which data were available, some rivers show positive trends in survival in the
first winter at sea (\So) while other show highly variable yet stable trends, and some even show
declines. We could not assess trends in the second winter at sea (\So) or
proportion returning as grilse (\Pg), as these parameter estimates were highly
uncertain and were strongly influenced by the priors used.
Perhaps there is a need to rethink our understanding of Atlantic salmon
population dynamics in light of the possibility that any real and persistent decline in marine survival was
experienced by some but not all populations, that reductions in survival might
have occurred over a relatively brief period of time and may not longer be ongoing, and that since that
reduction occurred (for a subset of populations) marine survival has
been stable, or even increasing.
